Verifying Demonstrations

### 2017-09-20 intro.tex
Minor edits
Adds clarifications, improves slides
Removes transitive trust, excessive examples
Changes to use \mode instead of implicit specs
Moves things around in the intro and to the intro
Moves overview of desired properties to intro, then the desired
properties section will be rewritten as more technically detailed.

Alice organizes a street protest against Eve's regime.
Bob, Carol and many others participate in the demonstration.
One problem that has not yet been entirely solved is the crowd-counting 
problem, i.e.\ to verify how many participated in Alice's protest.

\subsection<presentation>{What's the problem?}

@@

\subsection<presentation>{Why is it a problem?}

\mode<presentation>{%
\begin{frame}
  \begin{example}
    \begin{itemize}
      \item Computer vision does object recognition.
      \item Requires photos/video that cover the entire location, all the time.
      \item This will count people twice.
    \end{itemize}
  \end{example}

@@

\mode<presentation>{%
\begin{frame}
  \begin{example}
    \begin{itemize}
      \item South Korea 2016~\cite{2016DemonstrationsInSeoul}:
        approximate count by imagery.
        \begin{description}
          \item[Organizers] 1\,000\,000
          \item[Police] 260\,000
        \end{description}

@@

After many demonstrations the count by police and that by the organizers 
differ\footnote{%
  This is actually quite natural, they have different goals.
  The organizers want to count everyone who ever participated.
  Police want to estimate the count at the peak of participation, due to crowd 
  control~\cite{2016DemonstrationsInSeoul}.
}, in some instances the difference can be hundreds of thousands.
There are numerous examples, e.g.\ the demonstrations in South 
Korea~\cite{2016DemonstrationsInSeoul}, Trump's 
inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize} or the Women's Marches 
in the US~\cite{2017WomensMarchesInUS}, where there is difficulty in 
establishing the actual number of participants.
The methods for counting the crowds vary.
Most of the available methods lack precision, i.e.\ they have large error 
margins.
They can only give an estimate for a particular snapshot in time, e.g.\ at the 
peak of the event, not the cumulative participation count --- at least not 
without counting some people multiple times, which in turn increases the error 
of the estimation.
Finally, they also lack verifiability, i.e.\ everyone must trust the entity who
does the counting.
We will discuss them in more detail in \cref{RelatedWork}.

@@

      \item {\color{red} Eve wants to show that few support Alice's cause.}

      \item It's an adversarial setting!
      \item We need verifiable results.
    \end{itemize}
  \end{block}
\end{frame}

We can make one important observation about this problem that has seemingly 
been ignored in the past: it is an adversarial setting.
The protesters (organizers and participants) have an incentive to increase the 
tallied number of participants, whereas other interests might have an incentive 
to decrease the tallied number of participants, e.g.\ Eve's authoritarian 
regime in our example above.
Or the other way around, sometimes Eve's authoritarian regime wants to organize 
a pro-regime protest to demonstrate its \enquote{wide 
  support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
(This makes it difficult to rely on government-issued credentials to prevent a 
Sybil attack --- government can issue arbitrarily many such credentials for its 
own protests.)
To solve this problem, we need a verifiable participation count which is 
protected from Sybil attacks.

\subsection<article>{Contributions}

@@

>>>>

Alice is an activist who organizes a protest for some cause.
Eve is an autocrat who opposes Alice's cause.
Bob, Carol and many others participate in the protest against Eve.
One problem that has not yet been entirely solved is the crowd-counting 
problem, i.e.\ to verify how many participated in Alice's protest.
Our main goal is to provide a tool which prevents both Alice and Eve from 
cheating.

\mode<presentation>{%
\subsection{What's the problem?}
}

@@

\mode<presentation>{%
\subsection{Why is it a problem?}
}

\mode<presentation>{%
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/Jacobs-method.jpg}
  \end{figure}
\end{frame}

\begin{frame}
  \begin{example}
    \begin{itemize}
      \item Computer vision does object recognition.
      \item Requires photos/video that cover the entire location, all the time.
      \item This will count people twice.
    \end{itemize}
  \end{example}

@@

\mode<none>{%
\begin{frame}
  \begin{example}
    \begin{itemize}
      \item South Korea 2016~\cite{2016DemonstrationsInSeoul}:
        approximate count by imagery.
        \begin{description}
          \item[Organizers] 1\,000\,000
          \item[Police] 260\,000
        \end{description}

@@

After many demonstrations the count by police and that by the organizers 
differ\footnote{%
  This is actually quite natural, they have different goals.
  The organizers want to count everyone who ever participated.
  Police want to estimate the count at the peak of participation, due to crowd 
  control~\cite{2016DemonstrationsInSeoul}.
}, in some instances the difference can be hundreds of thousands.
There are numerous examples, e.g.\ the demonstrations in South 
Korea~\cite{2016DemonstrationsInSeoul}, Trump's 
inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize} or the Women's Marches 
in the US~\cite{2017WomensMarchesInUS}, where there is difficulty in 
establishing the actual number of participants.
The methods for counting the crowds vary.
Most of the available methods lack precision, i.e.\ they have large error 
margins.
They can only give an estimate for a particular snapshot in time, e.g.\ at the 
peak of the event, not the cumulative participation count --- at least not 
without counting some people multiple times, which in turn increases the error 
of the estimation.
Finally, they also lack verifiability, i.e.\ everyone must trust the entity who
does the counting.
(We will discuss them in more detail in \cref{RelatedWork}.)

@@

      \item {\color{red} Eve wants to show that few support Alice's cause.}
      \item It's an adversarial setting!
      \item We need verifiable results.
    \end{itemize}
  \end{block}
\end{frame}

We can make one important observation about this problem that has seemingly 
been ignored in the past: it is an adversarial setting.
The protesters (organizers and participants) have an incentive to increase the 
tallied number of participants, whereas other interests might have an incentive 
to decrease the tallied number of participants, e.g.\ Eve's authoritarian 
regime in our example above.
To solve this problem, we need a verifiable participation count which is 
protected from Sybil attacks.

\subsection{Combining electronic voting and location proofs}

Electronic voting (and voting in general) require strong verifiability and 
privacy properties.
We will adapt these requirements to the setting of protests.

There are three requirements for 
verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{frame}
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
  cast is legitimate.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the cast votes.
\item\label{IndividualVerif} Individual verifiability: every voter can verify 
  that their vote is included in the result.
\end{requirements}
\end{frame}
We translate the votes into \emph{proofs of participation}.
Both universal and individual verifiability remain the same.
The eligibility requirement is slightly different:
for protests the eligibility requirement must include temporal and spatial 
eligibility --- that each proof of participation satisfies some temporal and 
spatial relation to the protest.
We will define these more formally in \cref{Verification}.

There are also three requirements for 
privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{frame}
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
  individual vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\pause{}
\mode<presentation>{%
  \begin{remark}
    P\ref{CoercionResistance} \(\implies\)
    P\ref{ReceiptFreeness} \(\implies\)
    P\ref{VotePrivacy}
  \end{remark}
}
\end{frame}
\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
We note that we cannot improve the privacy of participating protesters, if they 
are caught during a protest there is nothing we can do.
But if they participate and they are not caught, then using our proposed tool 
should not incur any additional risk.
Thus we will adapt the idea of receipt freeness (see \cref{Privacy} for a 
detailed definition).
In essence, upon completing the protocol, Alice will have nothing that Eve can 
use to tie her to her participation proof.

\subsection{Contributions}

@@

Sometimes Eve's authoritarian regime wants to organize a pro-regime protest to 
demonstrate its \enquote{wide 
  support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
If we rely on government-issued credentials, we cannot prevent the government 
from performing Sybil attacks --- since it can issue arbitrarily many 
\enquote{valid} credentials.
This means that we cannot verify any pro-government protests.

### 2017-09-20 properties.tex
Changes section title of security analysis
Moves things around in the intro and to the intro
Moves overview of desired properties to intro, then the desired
properties section will be rewritten as more technically detailed.

\mode*
\section{The idea}%
\label{TheIdea}

Alice is an activist who organizes a demonstration for some cause.
Her main goal after the protest is to provide verifiable data.
There are several problems:
\begin{itemize}
  \item Alice must prove that the data is related to the event, that it is not 
    reused data from previous protests.
  \item Alice must provide data which can be used for the desired verification.
  \item Alice must also consider the privacy of the participating individuals.
\end{itemize}

\begin{frame}<presentation>
  \begin{itemize}
    \item Alice must prove that the data is related to the event.
    \item Alice must provide data with verifiable properties.
    \item Alice must consider the privacy of the participants.
  \end{itemize}
\end{frame}

Since many of the current techniques are based on photos, we will give an 
example of Alice's problems in that setting.
How can she ensure that photos from a demonstration are authentic?
We can probably recognize the location that the photo is portraying, however, 
this might just as well be a reconstruction or entirely computer generated.
We cannot trust the meta-data of the photo, such as time-stamps of the file, 
because these can easily be manipulated.
So the only thing we can say for sure is that the photo was taken at the latest 
at the time of publication.
Now, if we cannot trust these photos, how can we determine the number of 
participants of a demonstration?
Furthermore, how can Alice protect the privacy of those in the photos?

%However, to complicate things further,
%\blockcquote{VenezuelanStateWorkersCalledToParticipate}{%
%  \textins*{m}any of Venezuela’s 2.8 million state workers have reported 
%  getting text messages, phone calls and being required to attend political 
%  rallies during work hours
%}.
%
%\blockcquote{BBConVenezuelaProtestBan}{%
%  Venezuela is banning protests that could "disturb or affect" Sunday's 
%  controversial election for a new constituent assembly.
%}
%
%\blockcquote{BBConVenezuelaProtestBan}{%
%  Prison terms of between five and 10 years could be imposed on those 
%  contravening the ban,
%}
%
%\blockcquote{VenezuelanGovtBansProtesting}{%
%  Venezuelans are planning to defy a government ban on public demonstrations 
%  and risk deadly repression with marches across the country to protest against 
%  a vote Sunday that opposition forces say will mark the end of democracy
%}

>>>>

\mode*
\section{Desired properties}%
\label{TheIdea}
